---
title: "Data Analysis"
author: "Joel Larwood"
date: "30/04/2019"
output: github_document 
---

Data from clinical population to be reanalysed post stakeholder report. Only relevant data has been retained and amde public from previous deindetification script. 

```{r message = FALSE}
library(tidyverse)
library(knitr)
library(psych)
library(apa)
```

```{r message = FALSE}
cs <- read_csv("CIID_PublicData.csv")
names(cs)
```

#Missing data 
```{r}
missvar <- data.frame(nacount=colSums(is.na(cs)))
missvar$pctNA <- (missvar$nacount/(nrow(cs)))*100

missp <- data.frame(row.names = cs$id, nacount=rowSums(is.na(cs)))

missp$pctNA <- (missp$nacount/ncol(cs))*100

knitr::kable(missvar)
knitr::kable(missp)

```

###AQoL
Script converted from .sps file "v11_6D_DOL_alg_140114.sps"

#### Set up dimensions
####Independent Living 
```{r}
cIL <- c("Aqol1_1", "Aqol2_1", "Aqol3_1", "Aqol4_1")
```

####Relationships 
```{r}
cRL <- c("Aqol5_1", "Aqol6_1", "Aqol7_1")
```

####Mental Health
```{r}
cMH <- c("Aqol8_1", "Aqol9_1", "Aqol10_1", "Aqol11_1")
```

####Coping
```{r}
cCOP <- c("Aqol12_1", "Aqol13_1", "Aqol14_1")
```

####Pain
```{r}
cPAIN <- c("Aqol15_1", "Aqol16_1", "Aqol17_1")
```

####Senses 
```{r}
cSEN <- c("Aqol18_1", "Aqol19_1", "Aqol20_1")
```

###Missing data and impute 

####Calculate Missing Per Dimension
```{r}
cs$ILMiss <- cs %>% select(cIL) %>% is.na() %>% rowSums()
cs$RLMiss <- cs %>% select(cRL) %>% is.na() %>% rowSums()
cs$MHMiss <- cs %>% select(cMH) %>% is.na() %>% rowSums()
cs$COPMiss <- cs %>% select(cCOP) %>% is.na() %>% rowSums()
cs$PAINMiss <- cs %>% select(cPAIN) %>% is.na() %>% rowSums()
cs$SENMiss <- cs %>% select(cSEN) %>% is.na() %>% rowSums()
```


####Calculate rounded mean per dimension
```{r}

cs$ILMean <- cs %>% select(cIL, ILMiss)  %>% rowMeans(na.rm=TRUE) %>% round()
cs$RLMean <- cs %>% select(cRL, RLMiss)  %>% rowMeans(na.rm=TRUE) %>% round()
cs$MHMean <- cs %>% select(cMH)  %>% rowMeans(na.rm=TRUE) %>% round()
cs$COPMean <- cs %>% select(cCOP)  %>%  rowMeans(na.rm=TRUE) %>% round()
cs$PAINMean <- cs %>% select(cPAIN)  %>%rowMeans(na.rm=TRUE) %>% round()
cs$SENMean <- cs %>% select(cSEN)  %>%rowMeans(na.rm=TRUE) %>% round()

cs %>% select(contains("Mean")) %>% head(50)
```

###Impute rounded means 
When there is only 1 missing value replace that value with the rounded mean 

```{r}

cs %>% select(cIL, ILMean, ILMiss) %>% filter(ILMiss == 1) %>% head(50)
cs$Aqol4_1 <- ifelse(is.na(cs$Aqol4_1), cs$ILMean, cs$Aqol4_1)

cs %>% select(cRL, RLMean, RLMiss) %>% filter(RLMiss == 1) %>% head(50)
cs$Aqol7_1 <- ifelse (is.na(cs$Aqol7_1), cs$MHMean, cs$Aqol7_1)

cs %>% select(cMH, MHMean, MHMiss) %>% filter(MHMiss == 1) %>% head(50)

cs$Aqol11_1 <- ifelse (is.na(cs$Aqol11_1), cs$MHMean, cs$Aqol11_1)

cs %>% select(cCOP, COPMean, COPMiss) %>% filter(COPMiss == 1) %>% head(50)
cs %>% select(cPAIN, PAINMean, PAINMiss) %>% filter(PAINMiss == 1) %>% head(50)
cs %>% select(cSEN,SENMean, SENMiss) %>% filter(SENMiss == 1) %>% head(50)
cs$Aqol18_1 <- ifelse (is.na(cs$Aqol18_1), cs$SENMean, cs$Aqol18_1)
cs$Aqol20_1 <- ifelse(is.na(cs$Aqol20_1), cs$SENMean, cs$Aqol20_1)
```

###MUSE 
####Missing Per Participant
```{r}
cs$MUSEMiss <- cs %>% select(contains("MUSE")) %>% is.na() %>% rowSums()

cs %>% select(id, 
              contains("MUSE")) %>% filter(MUSEMiss > 0) %>% kable(caption = "Participants with missing MUSE data")
```

All mising MUSE data have whole scale unanswered

#Scores
##AQoL
###Get dimension scores 
```{r}
cs$ILtot <-  cs %>% select(cIL) %>% rowSums()
cs$RLtot <-  cs %>% select(cRL) %>% rowSums()
cs$MHtot <-  cs %>% select(cMH) %>% rowSums()
cs$COPtot <-  cs %>% select(cCOP) %>% rowSums()
cs$PAINtot <-  cs %>% select(cPAIN) %>% rowSums()
cs$SENtot <-  cs %>% select(cSEN) %>% rowSums()

cs %>% select(id, ILtot, RLtot, MHtot, COPtot, PAINtot, SENtot) %>% kable()
```
###Reliability 

```{r eval=TRUE}
aIL <- cs %>% select(cIL) %>% alpha()
print(aIL$total$std.alpha)
aRL <- cs %>% select(cRL) %>% alpha()
print(aRL$total$std.alpha)

aMH <- cs %>% select(cMH) %>% alpha()
print(aMH$total$std.alpha)

aCOP <- cs %>% select(cCOP) %>% alpha()
print(aCOP$total$std.alpha)

aPAIN <- cs %>% select(cPAIN) %>% alpha()
print(aPAIN$total$std.alpha)

aSEN <- cs %>% select(cSEN) %>% alpha()
print(aSEN$total$std.alpha)

```


##Toronto Alexithymia Scale 
###Scores 
```{r}
cs %>% select(contains("TAS")) %>% names()

cDID <- c("TAS1_1" , "TAS3_1" , "TAS6_1" , "TAS7_1" , "TAS9_1" , "TAS13_1" , "TAS14_1")
cDDF <- c("TAS2_1" ,"TAS4_1R","TAS11_1","TAS12_1","TAS17_1")
cEOT <- c("TAS5_1R" , "TAS8_1" , "TAS10_1R" , "TAS15_1" , "TAS18_1R" , "TAS19_1R" , "TAS20_1")

cs <- cs %>% mutate(DID = cs %>% select(cDID) %>% rowSums()
                    ,DDF = cs %>% select(cDDF) %>% rowSums()
                    ,EOT = cs %>% select(cEOT) %>% rowSums()
                    ,Alexithymia = DID + DDF + EOT)

names(cs) 
```
###Alpha
```{r}
aDID <- cs %>% select(cDID) %>% alpha() 
print(aDID$total$std.alpha)
aDDF <- cs %>% select(cDDF) %>% alpha()
print(aDDF$total$std.alpha)
aEOT <- cs %>% select(cEOT) %>% alpha()
print(aEOT$total$std.alpha)
```

##Music Use Scale 
###Scores
```{r}
cMUSEcog <- c("MUSE1_1", "MUSE2_1", "MUSE3_1", "MUSE4_1", "MUSE5_1", "MUSE6_1", "MUSE7_1")
cMUSEsoc <- c("MUSE8_1", "MUSE9_1", "MUSE10_1")

cs <- cs %>% mutate(MUSEcog = cs %>% select(cMUSEcog) %>% rowSums(),
                    MUSEsoc = cs %>% select(cMUSEsoc) %>% rowSums()) 
```

###Alpha 
```{r}
aMUSEcog <- cs %>% select(cMUSEcog) %>% alpha()
print(aMUSEcog$total$std.alpha)
aMUSEsoc <- cs %>% select(cMUSEsoc) %>% alpha()
print(aMUSEsoc$total$std.alpha)
```


# DERS 
## Due to time constrainsts the DERS was shorted to 4 items that loaded highest onto the factor

```{r ders}
cs <- cs %>% mutate(DERS = rowSums(select(., DERS6_1_1:DERS6_6_1)))

aDERS <- cs %>% select(DERS6_1_1:DERS6_6_1) %>% alpha()
aDERS$total$std.alpha
```

#Get descriptives 
```{r}
csInterestVars <- cs %>% select(Alexithymia,
              DID,
              DDF,
              EOT,
              ILtot,
              RLtot,
              MHtot,
              COPtot,
              PAINtot,
              SENtot,
              MUSEsoc,
              MUSEcog,
              DERS,
              Hours_listening_music,
              Days_a_week_listen_music) 

csInterestVars %>% skimr::skim() %>% skimr::kable()
```

```{r correlations}

visdat::vis_dat(csInterestVars)


csInterestVarsRename <- csInterestVars %>% 
  rename(TAS = Alexithymia,
         IL = ILtot,
         RL = RLtot,
         MH = MHtot,
         COP = COPtot,
         PAIN = PAINtot,
         SEN = SENtot,
         MUSE_S = MUSEsoc,
         MUSE_c = MUSEcog,
         Hours = Hours_listening_music,
         Days = Days_a_week_listen_music)

corrplot::corrplot(corr = (cor(csInterestVarsRename, use = "pairwise.complete.obs")),
                   method = "ellipse",
                   diag = FALSE,
                   type = "upper",
                   sig.level = .05,
                   insig = "blank",
                   p.mat = corrplot::cor.mtest(csInterestVarsRename, conf.level = .95)$p,
                   number.cex= 7/ncol(csInterestVarsRename),
                   tl.cex = 20/nrow(csInterestVarsRename),
                   )



corrplot::corrplot(corr = (cor(csInterestVarsRename, use = "pairwise.complete.obs")),
                   method = "number",
                   diag = FALSE,
                   type = "lower",
                   sig.level = .05,
                   insig = "blank",
                   p.mat = corrplot::cor.mtest(csInterestVarsRename, conf.level = .95)$p, 
                   number.cex= 7/ncol(csInterestVarsRename),
                   tl.cex = 20/nrow(csInterestVarsRename)
                   )


apaTables::apa.cor.table(csInterestVars)
```

